Catching Up With Republicans: Democratic Marriage Rates Are on the Rise

### 2023-11-28 outputs/paper.qmd
fixed typo in title
fixed typo

---
title: "Cathing Up With Republicans: Democratic Marriage Rates Are on the Rise"
subtitle: "An Analysis of 2014-2021 U.S. General Social Survey Data"
author: 
  - Chloe Thierstein
thanks: "Code and data are available at: https://github.com/cthierst/marital_status_politics_gss_analysis.git"
date: "April 20, 2023"
date-format: "D MMMM YYYY"
abstract: "Political identification is an important indicator of marital status within the United States and helps develop understandings of solidarity and division within the U.S. This paper investigates the relationship between political identification and marital status using four years of data from the U.S. General Social Survey. The analysis of this data reveals that marriages among left-leaning U.S. citizens is on the rise despite variances in the reporting of political identification."
format: pdf
toc: TRUE
number-sections: TRUE
bibliography: references.bib
---

@@

```{r}
#| include: false
#| message: false
#### Creating Graph for comparison 2018 respondent's generational cohort against marital status ####
cohort_marital_2018 <- ggplot(data=cleaned_gss_2018, aes(x = cohort, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "enerational Cohort",
    y = "# of Respondents ",
    fill = "Marital Status",
    caption = "2018 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") + 
  theme(text = element_text(size=6))
```

>>>>

---
title: "Catching Up With Republicans: Democratic Marriage Rates Are on the Rise"
subtitle: "An Analysis of 2014-2021 U.S. General Social Survey Data"
author: 
  - Chloe Thierstein
thanks: "Code and data are available at: https://github.com/cthierst/marital_status_politics_gss_analysis.git"
date: "April 20, 2023"
date-format: "D MMMM YYYY"
abstract: "Political identification is an important indicator of marital status within the United States and helps develop understandings of solidarity and division within the U.S. This paper investigates the relationship between political identification and marital status using four years of data from the U.S. General Social Survey. The analysis of this data reveals that marriages among left-leaning U.S. citizens is on the rise despite variances in the reporting of political identification."
format: pdf
toc: TRUE
number-sections: TRUE
bibliography: references.bib
---

@@

```{r}
#| include: false
#| message: false
#### Creating Graph for comparison 2018 respondent's generational cohort against marital status ####
cohort_marital_2018 <- ggplot(data=cleaned_gss_2018, aes(x = cohort, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Generational Cohort",
    y = "# of Respondents ",
    fill = "Marital Status",
    caption = "2018 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") + 
  theme(text = element_text(size=6))
```
